### 2015-06-29 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: Minor changes to hose stream report and plotting script; new drawings for specific hose tests

\chapter{Introduction}
\label{chap:Introduction}
NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire. The studies have resulted in guidance to the fire service regarding ventilation tactics. However, ventilation tactics alone will not result in the complete extinguishment of the fire; fire suppression with hose streams are needed.

@@

\section{Experimental Structure}
\label{sec:Experimental_Structure}
This series of field experiments was conducted into two structures located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.

\subsection{Construction}
\label{sec:Construction}
Two concrete structures were built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}. They were designed to simulate a single story and a two story residential structure.  The first floor of each structure had an outer wall composed of interlocking concrete blocks 0.61 m (2 ft) wide, 0.61 m (2 ft) high and 1.22 m (4 ft) long. The interior dimensions of each structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.  The joints and gaps between the blocks were filled with high temperature insulation.

The interior walls of the first floor or each structure were framed with steel studs and track.  The studs were set to 0.40 m (16 in) centers.  The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in) depth.  The TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.125 in) x 44 mm (1.75 in) and an 11 mm (0.43 in) thick oriented strand board web as shown in Figure  XX .  Tongue and grove, 18.3 mm (0.72 in) thick, oriented strand board was screwed (nailed?) to the top of the TJIs.

@@

Opening front door, window, rear doors.

Single story  
The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.  The ceiling of the burn room was the exposed ``floor assembly".  The walls of the hallway and entry foyer were composed of 16 mm (0.625 in) Type X gypsum room. The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.

@@

\section{Uncertainty}
\label{sec:Uncertainty}
There are different components of uncertainty in the length, differential pressure, and gas velocity reported here. Uncertainties are grouped into two categories according to the method used to estimate them. Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means ~\cite{Taylor&Kuyatt:1994}. Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100\%. After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty. Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95\% confidence interval (2$\sigma$). For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications. For other components, referenced research results and past experience with the instruments provided input in the uncertainty determination.

@@

Tests 16 and 17 followed an identical procedure that involved flowing water in a straight stream, narrow fog stream, and wide fog stream pattern from a monitor with a combination nozzle located at the south side, double doors on the first level of the West Structure. The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Tests 16 and 17 repeated an identical process three times, one time for each hose stream pattern. To begin the process, the nozzle was adjusted to produce the desired hose stream pattern. Once the nozzle was adjusted, water was applied at the ``far target", located on the ceiling approximately X m (Xft) from the south interior wall, for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. 60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds. Then, water flow stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the ``near target", located approximately on the ceiling X m (Xft) from the interior wall of the double doors (Fig.~\ref{fig:Test_16_17}).

@@

Tests 31 and 32 followed an identical procedure that involved flowing water from the north side double doors using a handline with a combination nozzle. A straight stream pattern was used during Test 31, and a narrow fog stream pattern was used during Test 32. Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_29-32_setup}) in the fixed position. After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction and then returned to the fixed position of 30 seconds. Next, the nozzle was rotated in the counter-clockwise direction for 30 seconds, and then returned to the fixed position for 30 seconds. While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated. After the patterns were applied with the south side door opened, the door was closed, the handline was aimed at Door BC, and each pattern was applied again for thirty seconds while the south side door was opened and closed. This entire procedure was repeated an additional time.

@@

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations for Tests 16 and 17}
\begin{tabular}{|l|c|c|c|c|}
\cline{2-5}
\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
\textit{Straight} & 
%%%%Test 16%%%% 
0.8 $\pm 0.2$ & 0.9 $\pm 0.2$ & 
%%%%Test 17%%%% 
0.7 $\pm 0.1$ & 0.7 $\pm 0.2$ \\ \hline
\textit{Narrow Fog} & 
%%%%Test 16%%%% 
1.4 $\pm 0.1$ & 1.0 $\pm 0.1$ & 
%%%%Test 17%%%% 
0.8 $\pm 0.2$ & 0.8 $\pm 0.1 $ \\ \hline
\textit{Wide Fog} 	& 
%%%%Test 16%%%% 
1.2 $\pm 0.1$ & 1.4 $\pm 0.1$ & 
%%%%Test 17%%%% 
0.9 $\pm 0.2$ & 0.7 $\pm 0.2$ \\ \hline
\end{tabular}
\label{table:Tests_16_17_BDP_A10_Avgs}
\end{table}

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations for Tests 16 and 17}
\begin{tabular}{|l|c|c|c|c|}
\cline{2-5}
\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
\textit{Straight} 	& 
%%%%Test 16%%%% 
2.8 $\pm 0.6$ & 3.1 $\pm 0.5$ & 
%%%%Test 17%%%% 
2.7 $\pm 0.4$ & 2.3 $\pm 0.8$ \\ \hline
\textit{Narrow Fog} & 
%%%%Test 16%%%% 
4.4 $\pm 0.3$ & 3.3 $\pm 0.4$ & 
%%%%Test 17%%%% 
2.6 $\pm 0.6$ & 2.7 $\pm 0.6$ \\ \hline
\textit{Wide Fog} 	& 
%%%%Test 16%%%% 
3.9 $\pm 0.5$ & 4.4 $\pm 0.3$ & 
%%%%Test 17%%%% 
3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ \\ \hline
\end{tabular}
\label{table:Tests_16_17_BDP_A13_Avgs}
\end{table}

@@

\begin{table}[!ht]
\addtolength{\tabcolsep}{-3.25pt}
\small
\caption{Average air velocity (m/s) through stairwell door for all hose stream and application pattern combinations for Tests 18 and 19}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
\cline{2-9}
\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textit{Straight} 	& 
%%%%Test 18%%%% 
-0.2 $\pm 0.3$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ & 
%%%%Test 19%%%% 
 0.0 $\pm 0.1$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ \\ \hline
\textit{Narrow Fog} & 
%%%%Test 18%%%% 
 0.4 $\pm 0.3$ & 1.0 $\pm 0.2$ & 0.8 $\pm 0.2$ & 1.0 $\pm 0.4$ & 
%%%%Test 19%%%% 
 1.2 $\pm 0.3$ & 1.2 $\pm 0.3$ & 1.1 $\pm 0.4$ & 1.2 $\pm 0.2$ \\ \hline
\textit{Wide Fog} 	& 
%%%%Test 18%%%% 
 0.9 $\pm 0.2$ & 0.9 $\pm 0.3$ & 0.9 $\pm 0.3$ & 0.8 $\pm 0.3$ & 
%%%%Test 19%%%% 
 1.0 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.9 $\pm 0.2$ & 0.9 $\pm 0.2$ \\ \hline
\end{tabular}
\label{table:Tests_18_19_BDP_A10_Avgs}
\end{table}

%code to increase resolution of tabulated values
%\textit{Straight} 	& -0.17 & 0.48 & 0.65 & 0.63 & -0.05 & 0.47 & 0.67 & 0.62 \\ \hline
%\textit{Narrow Fog} & 0.41 & 1.02 & 0.79 & 0.99 & 1.23 & 1.18 & 1.14 & 1.22 \\ \hline
%\textit{Wide Fog} 	& 0.93 & 0.90 & 0.91 & 0.75 & 0.96 & 0.67 & 0.89 & 0.93 \\ \hline

\begin{table}[!ht]
\addtolength{\tabcolsep}{-3.25pt}
\small
\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application pattern combinations for Tests 18 and 19}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
\cline{2-9}
\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textit{Straight}  &
%%%%Test 18%%%% 
-0.4 $\pm 1.3$ & 1.8 $\pm 1.1$ & 2.5 $\pm 1.1$ & 2.4 $\pm 0.8$ &
%%%%Test 19%%%%					
 0.2 $\pm 0.7$ & 1.6 $\pm 0.5$ & 2.5 $\pm 0.7$ & 2.1 $\pm 0.7$ \\ \hline
\textit{Narrow Fog} & 
%%%%Test 18%%%%
 1.3 $\pm 1.1$ & 3.6 $\pm 0.9$ & 2.6 $\pm 0.8$ & 3.5 $\pm 1.6$ & 
%%%%Test 19%%%%
 4.3 $\pm 1.0$ & 3.5 $\pm 1.0$ & 3.5 $\pm 1.5$ & 3.7 $\pm 0.9$ \\ \hline
\textit{Wide Fog} 	& 
%%%%Test 18%%%%
3.0 $\pm 0.7$ & 3.2 $\pm 1.0$ & 3.1 $\pm 1.1$ & 2.6 $\pm 1.3$ & 
%%%%Test 19%%%%
3.3 $\pm 0.7$ & 2.6 $\pm 0.6$ & 3.1 $\pm 0.6$ & 3.2 $\pm 0.5$ \\ \hline
\end{tabular}
\label{table:Tests_18_19_BDP_A13_Avgs}
\end{table}

%code to increase resolution of tabulated values
%\textit{Straight} 	& -0.43 & 1.75 & 2.46 & 2.40 & 0.20 & 1.60 & 2.47 & 2.10 \\ \hline
%\textit{Narrow Fog} & 1.34 & 3.61 & 2.55 & 3.48 & 4.26 & 3.48 & 3.49 & 3.66 \\ \hline
%\textit{Wide Fog} 	& 3.02 & 3.22 & 3.06 & 2.57 & 3.31 & 2.60 & 3.13 & 3.19 \\ \hline

@@

\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}

>>>>

\chapter{Introduction}
\label{chap:Introduction}
NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire. The studies have resulted in guidance to the fire service regarding ventilation tactics. However, ventilation tactics alone will not result in the complete extinguishment of the fire; fire suppression with hose streams is also needed.

@@

\section{Experimental Structure}
\label{sec:Experimental_Structure}
This series of field experiments was conducted in two structures located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.

\subsection{Construction}
\label{sec:Construction}
Two concrete structures were built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}. They were designed to simulate a single-story and a two-story residential structure.  The first floor of each structure had an outer wall composed of interlocking concrete blocks of dimensions 0.61 m x 0.61 m 0.61 m (2 ft x 2ft x 2ft). The interior dimensions of each structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.  The joints and gaps between the blocks were filled with high temperature insulation.

The interior walls of the first floor of each structure were framed with steel studs and track.  The studs were set to 0.40 m (16 in) centers.  The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in) depth.  The TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.125 in) x 44 mm (1.75 in) and an 11 mm (0.43 in) thick oriented strand board web as shown in Figure  XX .  Tongue and grove, 18.3 mm (0.72 in) thick, oriented strand board was screwed (nailed?) to the top of the TJIs.

@@

The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.  The ceiling of the burn room was the exposed ``floor assembly".  The walls of the hallway and entry foyer were composed of 16 mm (0.625 in) Type X gypsum room. The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.

@@

\section{Uncertainty}
\label{sec:Uncertainty}
There are different components of uncertainty in the length, differential pressure, and gas velocity reported here. Uncertainties are grouped into two categories according to the method used to estimate them. Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}. Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100\%. After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty. Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95\% confidence interval (2$\sigma$). For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications. For other components, referenced research results and past experience with the instruments provided input in the uncertainty determination.

@@

Tests 16 and 17 followed an identical procedure that involved flowing water in a straight stream, narrow fog stream, and wide fog stream pattern from a monitor with a combination nozzle located at the south side, double doors on the first level of the West Structure. The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Tests 16 and 17 repeated an identical process three times, one time for each hose stream pattern. To begin the process, the nozzle was adjusted to produce the desired hose stream pattern. Once the nozzle was adjusted, water was applied at the "far target", located on the ceiling approximately X m (Xft) from the south interior wall, for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. 60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds. Then, water flow stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the "near target", located approximately on the ceiling X m (Xft) from the interior wall of the double doors (Fig.~\ref{fig:Test_16_17}).

@@

Tests 31 and 32 followed an identical procedure that involved flowing water from the north side double doors using a handline with a combination nozzle. A straight stream pattern was used during Test 31, and a narrow fog stream pattern was used during Test 32. Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_31_32_setup}) in the fixed position. After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction and then returned to the fixed position of 30 seconds. Next, the nozzle was rotated in the counter-clockwise direction for 30 seconds, and then returned to the fixed position for 30 seconds. While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated. After the patterns were applied with the south side door opened, the door was closed, the handline was aimed at Door BC, and each pattern was applied again for 30 seconds while the south side door was opened and closed. This entire procedure was repeated an additional time.

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_31_32}
\caption[East Structure layout for Tests 31 and 32]{East Structure layout for Tests 31 and 32.}
\label{fig:Test_31_32_setup}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_34}
\caption[East Structure layout for Tests 31 and 32]{East Structure layout for Tests 31 and 32.}
\label{fig:Test_34_setup}
\end{figure}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%% ORIGINAL TABLES %%%%%%%%%%%%%%%%%%%%%%
%\begin{table}[!ht]
%\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations for Tests 16 and 17}
%\begin{tabular}{|l|c|c|c|c|}
%\cline{2-5}
%\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
%\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
%\textit{Straight} & 
%%%%%Test 16%%%% 
%0.8 $\pm 0.2$ & 0.9 $\pm 0.2$ & 
%%%%%Test 17%%%% 
%0.7 $\pm 0.1$ & 0.7 $\pm 0.2$ \\ \hline
%\textit{Narrow Fog} & 
%%%%%Test 16%%%% 
%1.4 $\pm 0.1$ & 1.0 $\pm 0.1$ & 
%%%%%Test 17%%%% 
%0.8 $\pm 0.2$ & 0.8 $\pm 0.1 $ \\ \hline
%\textit{Wide Fog} 	& 
%%%%%Test 16%%%% 
%1.2 $\pm 0.1$ & 1.4 $\pm 0.1$ & 
%%%%%Test 17%%%% 
%0.9 $\pm 0.2$ & 0.7 $\pm 0.2$ \\ \hline
%\end{tabular}
%\label{table:Tests_16_17_BDP_A10_Avgs}
%\end{table}

%\begin{table}[!ht]
%\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations for Tests 16 and 17}
%\begin{tabular}{|l|c|c|c|c|}
%\cline{2-5}
%\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
%\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
%\textit{Straight} 	& 
%%%%%Test 16%%%% 
%2.8 $\pm 0.6$ & 3.1 $\pm 0.5$ & 
%%%%%Test 17%%%% 
%2.7 $\pm 0.4$ & 2.3 $\pm 0.8$ \\ \hline
%\textit{Narrow Fog} & 
%%%%%Test 16%%%% 
%4.4 $\pm 0.3$ & 3.3 $\pm 0.4$ & 
%%%%%Test 17%%%% 
%2.6 $\pm 0.6$ & 2.7 $\pm 0.6$ \\ \hline
%\textit{Wide Fog} 	& 
%%%%%Test 16%%%% 
%3.9 $\pm 0.5$ & 4.4 $\pm 0.3$ & 
%%%%%Test 17%%%% 
%3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ \\ \hline
%\end{tabular}
%\label{table:Tests_16_17_BDP_A13_Avgs}
%\end{table}

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations for Tests 16 and 17}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}}
\\
\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\
\midrule
\textit{Straight} & 
%%%%Test 16%%%% 
2.8 $\pm 0.6$ & 3.1 $\pm 0.5$ & 
%%%%Test 17%%%% 
2.7 $\pm 0.4$ & 2.3 $\pm 0.8$
\\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 16%%%% 
4.4 $\pm 0.3$ & 3.3 $\pm 0.4$ & 
%%%%Test 17%%%% 
2.6 $\pm 0.6$ & 2.7 $\pm 0.6$
\\	\multicolumn{5}{c}{}	\\
\textit{Wide Fog} 	& 
%%%%Test 16%%%% 
3.9 $\pm 0.5$ & 4.4 $\pm 0.3$ & 
%%%%Test 17%%%% 
3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ 
\\ 
\bottomrule
\end{tabular}
\label{table:Tests_16_17_BDP_A13_Avgs}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%% ORIGINAL TABLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{table}[!ht]
%\addtolength{\tabcolsep}{-3.25pt}
%\small
%\caption{Average air velocity (m/s) through stairwell door for all hose stream and application pattern combinations for Tests 18 and 19}
%\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
%\cline{2-9}
%\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
%\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\textit{Straight} 	& 
%%%%%Test 18%%%% 
%-0.2 $\pm 0.3$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ & 
%%%%%Test 19%%%% 
% 0.0 $\pm 0.1$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ \\ \hline
%\textit{Narrow Fog} & 
%%%%%Test 18%%%% 
% 0.4 $\pm 0.3$ & 1.0 $\pm 0.2$ & 0.8 $\pm 0.2$ & 1.0 $\pm 0.4$ & 
%%%%%Test 19%%%% 
% 1.2 $\pm 0.3$ & 1.2 $\pm 0.3$ & 1.1 $\pm 0.4$ & 1.2 $\pm 0.2$ \\ \hline
%\textit{Wide Fog} 	& 
%%%%%Test 18%%%% 
% 0.9 $\pm 0.2$ & 0.9 $\pm 0.3$ & 0.9 $\pm 0.3$ & 0.8 $\pm 0.3$ & 
%%%%%Test 19%%%% 
% 1.0 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.9 $\pm 0.2$ & 0.9 $\pm 0.2$ \\ \hline
%\end{tabular}
%\label{table:Tests_18_19_BDP_A10_Avgs}
%\end{table}
%
%%code to increase resolution of tabulated values
%%\textit{Straight} 	& -0.17 & 0.48 & 0.65 & 0.63 & -0.05 & 0.47 & 0.67 & 0.62 \\ \hline
%%\textit{Narrow Fog} & 0.41 & 1.02 & 0.79 & 0.99 & 1.23 & 1.18 & 1.14 & 1.22 \\ \hline
%%\textit{Wide Fog} 	& 0.93 & 0.90 & 0.91 & 0.75 & 0.96 & 0.67 & 0.89 & 0.93 \\ \hline
%
%\begin{table}[!ht]
%\addtolength{\tabcolsep}{-3.25pt}
%\small
%\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application pattern combinations for Tests 18 and 19}
%\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
%\cline{2-9}
%\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
%\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\textit{Straight}  &
%%%%%Test 18%%%% 
%-0.4 $\pm 1.3$ & 1.8 $\pm 1.1$ & 2.5 $\pm 1.1$ & 2.4 $\pm 0.8$ &
%%%%%Test 19%%%%					
% 0.2 $\pm 0.7$ & 1.6 $\pm 0.5$ & 2.5 $\pm 0.7$ & 2.1 $\pm 0.7$ \\ \hline
%\textit{Narrow Fog} & 
%%%%%Test 18%%%%
% 1.3 $\pm 1.1$ & 3.6 $\pm 0.9$ & 2.6 $\pm 0.8$ & 3.5 $\pm 1.6$ & 
%%%%%Test 19%%%%
% 4.3 $\pm 1.0$ & 3.5 $\pm 1.0$ & 3.5 $\pm 1.5$ & 3.7 $\pm 0.9$ \\ \hline
%\textit{Wide Fog} 	& 
%%%%%Test 18%%%%
%3.0 $\pm 0.7$ & 3.2 $\pm 1.0$ & 3.1 $\pm 1.1$ & 2.6 $\pm 1.3$ & 
%%%%%Test 19%%%%
%3.3 $\pm 0.7$ & 2.6 $\pm 0.6$ & 3.1 $\pm 0.6$ & 3.2 $\pm 0.5$ \\ \hline
%\end{tabular}
%\label{table:Tests_18_19_BDP_A13_Avgs}
%\end{table}
%
%%code to increase resolution of tabulated values
%%\textit{Straight} 	& -0.43 & 1.75 & 2.46 & 2.40 & 0.20 & 1.60 & 2.47 & 2.10 \\ \hline
%%\textit{Narrow Fog} & 1.34 & 3.61 & 2.55 & 3.48 & 4.26 & 3.48 & 3.49 & 3.66 \\ \hline
%%\textit{Wide Fog} 	& 3.02 & 3.22 & 3.06 & 2.57 & 3.31 & 2.60 & 3.13 & 3.19 \\ \hline

\begin{table}[!ht]
%\addtolength{\tabcolsep}{-3.25pt}
%\small
\caption{Average air velocity (m/s) through stairwell door for all hose stream and application pattern combinations for Tests 18 and 19}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{4}{c}{\underline{Test 18}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\
\midrule 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textit{Straight} 	& 
%%%%Test 18%%%% 
-0.2 $\pm 0.3$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ 
\\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 18%%%% 
 0.4 $\pm 0.3$ & 1.0 $\pm 0.2$ & 0.8 $\pm 0.2$ & 1.0 $\pm 0.4$ 
\\	\multicolumn{5}{c}{}	\\
\textit{Wide Fog} 	& 
%%%%Test 18%%%% 
 0.9 $\pm 0.2$ & 0.9 $\pm 0.3$ & 0.9 $\pm 0.3$ & 0.8 $\pm 0.3$ 
\\
\midrule
& \multicolumn{4}{c}{\underline{Test 19}} 
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\
\midrule
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textit{Straight} 	& 
%%%%Test 19%%%% 
 0.0 $\pm 0.1$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ 
\\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 19%%%% 
 1.2 $\pm 0.3$ & 1.2 $\pm 0.3$ & 1.1 $\pm 0.4$ & 1.2 $\pm 0.2$
\\	\multicolumn{5}{c}{}	\\
\textit{Wide Fog} 	& 
%%%%Test 19%%%% 
 1.0 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.9 $\pm 0.2$ & 0.9 $\pm 0.2$
\\
\bottomrule
\end{tabular}
\label{table:Tests_18_19_BDP_A10_Avgs}
\end{table}

\begin{table}[!ht]
%\addtolength{\tabcolsep}{-3.25pt}
%\small
\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application pattern combinations for Tests 18 and 19}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{4}{c}{\underline{Test 18}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\
\midrule 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textit{Straight}  &
%%%%Test 18%%%% 
-0.4 $\pm 1.3$ & 1.8 $\pm 1.1$ & 2.5 $\pm 1.1$ & 2.4 $\pm 0.8$
\\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 18%%%%
 1.3 $\pm 1.1$ & 3.6 $\pm 0.9$ & 2.6 $\pm 0.8$ & 3.5 $\pm 1.6$
 \\	\multicolumn{5}{c}{}	\\ 
\textit{Wide Fog} 	& 
%%%%Test 18%%%%
3.0 $\pm 0.7$ & 3.2 $\pm 1.0$ & 3.1 $\pm 1.1$ & 2.6 $\pm 1.3$
\\
\midrule
 & \multicolumn{4}{c}{\underline{Test 19}}	\\ 
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\
\midrule
\textit{Straight}  &
%%%%Test 19%%%%					
 0.2 $\pm 0.7$ & 1.6 $\pm 0.5$ & 2.5 $\pm 0.7$ & 2.1 $\pm 0.7$ 
 \\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 19%%%%
 4.3 $\pm 1.0$ & 3.5 $\pm 1.0$ & 3.5 $\pm 1.5$ & 3.7 $\pm 0.9$
\\	\multicolumn{5}{c}{}	\\
\textit{Wide Fog} 	& 
%%%%Test 19%%%%
3.3 $\pm 0.7$ & 2.6 $\pm 0.6$ & 3.1 $\pm 0.6$ & 3.2 $\pm 0.5$
\\
\bottomrule
\end{tabular}
\label{table:Tests_18_19_BDP_A13_Avgs}
\end{table}

@@

\bibliography{../../../../../Bibliography/FDS_general}
